An agent-based model of interdisciplinary interactions in science

### 2020-06-22 Docs/Papers/ABMInterdisc/paper/paper.tex
arxiv_nw

\cite{101371journalpone0221907} assymetry of interdisc between social and hard sciences in the credit given to other disciplines

\cite{10.1371/journal.pbio.3000065} competition for funding is inefficient

@@

@@

Beyond the simplifying opposition between fully constructivist and realistic approaches to science, several alternatives have been developed, among which Perspectivism \cite{giere2010scientific} is a way to tackle most of the issues opposing these two by taking an agent-based approach to the production of scientific knowledge. The principal feature of this point of view is to consider each scientific enterprise as a single perspective, in which an agent aims to understand an aspect of the real world (the ontology) with the mean of a medium, that is considered as a model. Constituted disciplines thus contains more or less compatible perspectives. The explicitation of this approach has been done by~\cite{raimbault2017knowledge} to embed it into knowledge domains, as a generalization of knowledge domains introduced by~\cite{livet2010}.

@@

\cite{pluchino2018talent} role of randomness in individual trajectories success

@@

@@

>>>>

\cite{urbanska2019does} assymetry of interdisc between social and hard sciences in the credit given to other disciplines

\cite{gross2019contest} competition for funding is inefficient

@@

\subsection{Agent-based models of scientific knowledge production}

\cite{shafiee2019agent} use an agent-based model to simulate the impact of a workflow to process data under different collaboration scenarios.

\cite{doi10.1162qssa00008} simulate citation dynamics, and more particularly the consequence of introducing a performance index on citation patterns.

% peer review
\cite{feliciani2019scoping} surveys 46 simulation studies of peer review with numerous applications
\cite{kovanis2016complex}

@@

Beyond the simplifying opposition between fully constructivist and realistic approaches to science, several alternatives have been developed, among which Perspectivism \cite{giere2010scientific} is a way to tackle most of the issues opposing these two by taking an agent-based approach to the production of scientific knowledge. The principal feature of this point of view is to consider each scientific enterprise as a single perspective, in which an agent aims to understand an aspect of the real world (the ontology) with the mean of a medium, that is considered as a model. Constituted disciplines thus contains more or less compatible perspectives. The explicitation of this approach has been done by~\cite{raimbault2017knowledge} to embed it into knowledge domains, as a generalization of knowledge domains introduced by~\cite{livet2010ontology}.

@@

\cite{pluchino2019exploring} role of randomness in individual trajectories success

@@

\subsection{Rationale}

Many dimensions and processes are at play to shape collaborations between scientists and more broadly between scientific disciplines. These include for example social networks, governance and funding issues, or knowledge proximity (which can occur on various knowledge domains, from methodological to empirical or theoretical). Our rationale is to propose an agent-based model grasping some of this complexity from the bottom-up focusing on scientist behavior, but simple enough so that it can be systematically explored. We include thus in the model two basic antagonist processes, namely a propensity to collaborate mostly determined by knowledge proximity, and some resources constraints (time, funding) which affect negatively the possibility to collaborate. Working with scientists outside one's field has indeed a high cost, from finding common ground and research questions to an possible construction of integrated knowledge \cite{frodeman2013sustainable}.

\subsection{Model description}

@@

\subsection{Empirical data}

% arxiv https://arxiv.org/help/bulk_data
https://arxiv.org/pdf/1905.00075.pdf % citation network dataset
https://github.com/mattbierbaum/arxiv-public-datasets/releases

\subsection{Model exploration}
